### 2016-09-16 overlay_fs.tex

We notice that one GB is now available to be used in the partitions. Also, we
observe the new partition should start at sector 4806656. To create it, we
show the introduced command and its output:

\begin{lstlisting}[]
$ (echo n; echo p; echo 3; echo 4806656; echo ; echo w) | fdisk ${IMAGE}.img

Command (m for help): Partition type:
   p primary (1 primary, 0 extended, 3 free)
   e extended
Partition number (1-4, default 3): Using default value 3
First sector (2048-6903807, default 2048): Last sector, +sectors or
+size{K,M,G} (4806656-6903807, default 6903807): Using default value 6903807

Command (m for help): The partition table has been altered!

Syncing disks.
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

>>>>

We notice that one GB is now available to be used in the partitions. Also, we
observe the new partition should start at sector 4806656. To create it, we
show the introduced command:% and its output:

%\begin{lstlisting}[]
%$ (echo n; echo p; echo 3; echo 4806656; echo ; echo w) | fdisk ${IMAGE}.img
%
%Command (m for help): Partition type:
%   p primary (1 primary, 0 extended, 3 free)
%   e extended
%Partition number (1-4, default 3): Using default value 3
%First sector (2048-6903807, default 2048): Last sector, +sectors or
%+size{K,M,G} (4806656-6903807, default 6903807): Using default value 6903807
%
%Command (m for help): The partition table has been altered!
%
%Syncing disks.
%\end{lstlisting}
\begin{lstlisting}[]
$ fdisk ${IMAGE}.img <<EOF
n
p
3
4806656

w
EOF
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

%\textcolor{red}{SHOW NEW PARTITION TABLE HERE}
